### 2019-08-19 maciek.tex
Lower bound, simplifications

Consider clusters $A$ and $B$ that contain nodes $a_1, a_2, a_3$ and $b_1, b_2, b_3$, respectively.
The adversary begins with issuing three requests: $(a_1, a_2)$, $(b_1, b_2)$, and $(a_3, b_3)$.
Note that these require moving one of these pairs to a third cluster.
Our idea is that the OPT pays for the request $(a_3, b_3)$ only (i.e., it moves this pair to a cluster $D$), and for OPT all other requests are free.

The algorithm must place these three components in different clusters. Let's call the cluster of $(a_1, a_2)$ the cluster $A_{ALG}$, the cluster of $(b_1, b_2)$ the cluster $B_{ALG}$ and the cluster of $(a_3, b_3)$ the cluster $C$. The configuration of ALG's clusters is then: $A$ contains $a_1, a_2,x$, $B$ contains $b_1, b_2,y$ and $C$ contains $a_3, b_3, z$, for some $x, y, z$ (of choice of the algorithm).
For this, ALG pays at least $2$.

The OPT places these three components in clusters $A, B$ and $D$, paying $2$ for migrating $a_3$ and $b_3$. The OPT has the freedom of choice of the cluster $D$ depending on the choices of the algorithm. We choose $D$ in such way that it does not contain neither $x$ nor $y$, and furthermore that the algorithm places any of nodes from $D$ at $x$ or $y$'s place as the last possible move.
The configuration of OPT's clusters is then: $A$ contains $a_1, a_2,d_1$, $B$ contains $b_1, b_2,d_2$ and $D$ contains $a_3, b_3, d_3$.
Note that the requests between nodes of the same color are free for OPT, with the exception of nodes from $A$, $B$, and most notably $D$.

From this point, OPT does not change its configuration, and the adversary continues to issue a request between $x$ and any other node with the same color as $x$.
Upon receiving this request, ALG pays for it the cost $1$ and it increases its number of clusters that contain non-singleton components.
This procedure ends when ALG has no more clusters with singleton-only components left or ALG manages to put $d_1, d_2$ or $d_3$ in place of $x$ or $y$.

At the begining, ALG has $\ell$ singleton-only components and each request increases their number by $1$.
Furthermore, before reaching either $d_1, d_2$ or $d_3$ in place of $x$ or $y$, the algorithm must cycle through $\Omega(\ell)$ nodes from other clusters. This is guaranteed as the choice of $D$ can depend on the actions of the deterministic algorithm.
In total, OPT pays $2$, and ALG pays $\Omega(\ell)$ (for each request besides the first two).

>>>>

Consider clusters $A$ and $B$ that contain nodes $a_1, a_2, a_3$ and $b_1, b_2, b_3$, respectively.
The adversary begins with issuing three requests: $(a_1, a_2)$, $(b_1, b_2)$, and $(a_3, b_3)$.
Note that these require moving one of these pairs to a third cluster.
Our idea is that the OPT pays for the request $(a_3, b_3)$ only (i.e., it moves this pair to a carefuly chosen cluster, that we denote by $D$), and for OPT all other requests are free.

The algorithm must place these three components in different clusters. Let's call the cluster of $(a_1, a_2)$ the cluster $A_{ALG}$, the cluster of $(b_1, b_2)$ the cluster $B_{ALG}$ and the cluster of $(a_3, b_3)$ the cluster $C$. The configuration of ALG's clusters is then: $A_{ALG}$ contains $a_1, a_2,x$, the cluster $B_{ALG}$ contains $b_1, b_2,y$ and the cluster $C$ contains $a_3, b_3, z$, for some $x, y, z$ (of the algorithm's choice).
For this, ALG pays at least $2$.

The OPT places these three components in clusters $A, B$ and $D$, paying $2$ for migrating $a_3$ and $b_3$. The OPT has the freedom of choice of the cluster $D$ depending on the choices of the algorithm. We choose $D$ in such way that it does not contain neither $x$ nor $y$, and furthermore that the algorithm places any of nodes from $D$ at $x$'s or $y$'s place as the last possible move.
The configuration of OPT's clusters is then: $A$ contains $a_1, a_2,d_1$, $B$ contains $b_1, b_2,d_2$ and $D$ contains $a_3, b_3, d_3$.
Note that the requests between nodes of the same color are free for OPT, with the exception of nodes from $A$, $B$, and most notably $D$.

From this point, OPT does not change its configuration, and the adversary continues to issue a request between a node colocated with the pair $(a_1, a_2)$, which we call $x$ (we update $x$ in every iteration, as it gets moved from this place) and any other node with the same color as $x$.
Upon receiving this request, ALG pays for it the cost at least $1$ and it increases its number of clusters that contain non-singleton components by $1$.
This procedure ends when ALG has no more clusters with singleton-only components left or ALG manages to put $d_1, d_2$ or $d_3$ in place of either $x$ or $y$.

At the begining, ALG has $\ell$ singleton-only components and each request increases their number by $1$.
Furthermore, before reaching either $d_1, d_2$ or $d_3$ in place of either $x$ or $y$, the algorithm must cycle through $\Omega(\ell)$ nodes from other clusters. This is guaranteed as the choice of $D$ can depend on the actions of the deterministic algorithm.
In total, OPT pays $2$, and ALG pays $\Omega(\ell)$ (for each request besides the first two).
